%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Crystal Campbell} \\ \vspace{1pt}
     \small 417-379-1561 $|$ \href{cjkcampbell@gmail.com}{\underline{cjkcampbell@gmail.com}} $|$
    \href{https://www.linkedin.com/in/cjkcampbell/}{\underline{linkedin.com/in/cjkcampbell/}} $|$
    \href{https://github.com/LeelooMina}{\underline{github.com/LeelooMina}}
\end{center}


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart

    \resumeProjectHeading
      {\textbf{BitBucket Pipeline Visualizer} $|$ \emph{Vue.js, Node.js, Express.js, MongoDB, Javascript, BitBucket}}{}
          \resumeItemListStart
            \resumeItem{Developed a custom CI/CD dashboard to client specifications}
            \resumeItem{Implemented real-time visualization of CI/CD pipelines, enabling teams to track build statuses, duration, and success rates.}
            \resumeItem{Created and implemented an API and database to store user information, allowing users to create posts, like content, and follow other users.}
             \resumeItem{Ensured efficient data storage and retrieval using MongoDB for quick access to historical pipeline information.}
              \resumeItem{Collaborated with a team to deliver a high-quality solution within project deadlines.}
              \resumeItemListEnd
     \resumeProjectHeading
          {\textbf{Oak Tree (Twitter Clone)} $|$ \emph{Ruby on Rails, Bootstrap, Vanilla CSS, Railway}}{}
          \resumeItemListStart
            \resumeItem{Designed an ER diagram using draw.io to visually represent the database schema and entity relationships}
            \resumeItem{Developed an authentication system for user accounts.}
            \resumeItem{Created and implemented the database to store user information, allowing users to create posts, like content, and follow other users.}
             \resumeItem{Replicated Twitter's site design using Bootstrap and the CSS Flexbox system.}
              \resumeItem{Configured deployment settings for the application on Railway, including environment variables and troubleshooting via the command line.}
           
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{SocialCocktails} $|$ \emph{Angular, Bootstrap, Vanilla CSS, Firebase}}{}
          \resumeItemListStart
            \resumeItem{Collaborated with a team to build a social media site for cocktail recipes, integrating the CocktailDB API.}
            \resumeItem{Responsible for coding the implementation of the API}
            \resumeItem{Designed and developed the social feed feature.}
             \resumeItem{Implemented a favorites feature with options to share to the feed page.}
              \resumeItem{Enhanced the site's user experience with CSS and Angular animations for smooth transitions.}
               \resumeItem{Worked closely with the team to test, debug, and optimize the site.}
            \resumeItem{Provided guidance and support to team members facing challenging elements of the project.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{ProjectBox} $|$ \emph{Angular, Bulma, Firebase}}{}
          \resumeItemListStart
            \resumeItem{Designed a project management system to plan ideas, features, and track bugs.}
            \resumeItem{Utilized Google Login and Firebase authentication }
            \resumeItem{Implemented Firebase Realtime Database models for projects, tasks, and todos}
            \resumeItem{Crafted the site design to ensure a user-friendly interface.}
          \resumeItemListEnd
          \resumeProjectHeading
          {\textbf{Ruby Kingdom} $|$ \emph{Ruby, Firebase}}{}
          \resumeItemListStart
            \resumeItem{Developed a text-based adventure game with a command-line interface.}
            \resumeItem{Designed and programmed an interactive battle and leveling system}
            \resumeItem{Implemented a 2D array to craft a grid-based map that allows for player movement}
            \resumeItem{Utilized the Pokémon API to randomly name game enemies}
            \resumeItem{Incorporated Firebase authentication for planned features}
          \resumeItemListEnd
    \resumeSubHeadingListEnd


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
   \resumeSubheading
      {Codefi Code Labs}{Springfield, MO}
      {Back End Development}{Jan. 2023 -- Jun. 2023}
    \resumeSubheading
      {Codefi Code Labs}{Springfield, MO}
      {Front End Development}{Aug. 2022 -- Dec. 2022}
    \resumeSubheading
      {Ozark Technical Community College}{Springfield, MO}
      {Completed  36 credits towards A.A.S. Computer Information Science}{Jan. 2012 -- May 2014}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Associate Web Developer} {Jan. 2023 - Present}
      {Codefi}{Apprenticeship}
      \resumeItemListStart
        \resumeItem{Contributed to the development of a custom Learning Management System (LMS) }
\resumeItem{Acquired proficiency in Jira, agile principles and methodologies, participated in stand-up meetings, and sprint planning, ensuring effective collaboration within the team.}
\resumeItem{Gained practical experience in both front-end and back-end development, encompassing HTML, CSS, JavaScript, as well as API and database integration.}
      \resumeItemListEnd

    \resumeSubheading
      {Content Writer and Consultant}{Dec. 2013 -- Dec. 2022}
      {Freelance}{Remote}
      \resumeItemListStart
        \resumeItem{Worked with clients to develop content plans to suit their needs}
        \resumeItem{Researched topics to explore options, understand target markets, and to support the writing process}
        \resumeItem{Assisted clients in creating and implementing well-rounded web content strategies}
         \resumeItem{Educated prospects on realistic goals, budget limitations, and steps needed to implement ideals.}
            \resumeItem{Collaborated with other writers to deliver projects on a deadline}
      \resumeItemListEnd

         \resumeSubheading
      {Google Search Rater}{Jan. 2013 -- May 2016}
      {Lionbridge - NDA}{Contract}
      \resumeItemListStart
        \resumeItem{Evaluated and rated search engine results for Google to enhance the accuracy and relevance of search results.}
        \resumeItem{Applied guidelines provided by Google to assess the quality of web pages and their relevance to user queries.}
        \resumeItem{Analyzed search queries and search results to identify patterns and trends.}
         \resumeItem{Maintained confidentiality and followed strict ethical standards in handling sensitive information.}
            \resumeItem{Collaborated with other writers to deliver projects on a deadline}
      \resumeItemListEnd





%-----------VOLUNTEER-----------
\section{Volunteer}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Youth Coding League }{Fall 2022}
      {Technical Merit Judge}{}

       \resumeSubheading
      {Youth Coding League }{Spring 2023}
      {Technical Merit Judge}{}
    

        \resumeSubheading
      {Hack4Good}{2023}
      {Communications Committee}{}
     



      
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

  \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
    {HTML, CSS, JavaScript, TypeScript, Angular, Ruby, Rails 7, Node.js, Express.js, Vue.js, ASP.NET, Bootstrap, Bulma, Firebase, GitHub, BitBucket, Railway, Jira} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
